An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-03 indicators/paper/paper.tex
Tweak last intro paragraph

The Delphi group worked with partner organizations and public data sets to build
a large-scale database of indicators tracking COVID-19 activity and other
relevant phenomena in the United States, which has been publicly available and
continuously updated since April 2020. Alongside public data on reported cases
and deaths, this database includes several unique data streams, including
indicators extracted from de-identified medical claims data, antigen test
results from a major testing manufacturer, large-scale public surveys that
measure symptoms and public behavior, and indicators based on particular Google
search queries. (We use the terms ``indicator'' and ``signal'' interchangeably.)
We make aggregate signals publicly available, generally at the county level, via
the COVIDcast API \cite{CovidcastAPI}. We store and provide access to all
previous (historical) versions of the signals, a key feature that exposes the
effects of data revisions. Lastly, we provide R \cite{CovidcastR} and Python
\cite{CovidcastPy} packages to facilitate interaction with the API, and an
online dashboard to visualize the data \cite{CovidcastViz}.

In a companion paper, we analyze the utility provided by a core set of the
indicators in COVID-19 forecasting and hotspot prediction models
\cite{McDonald:2021}. In another companion paper, we elaborate on our research
group's (Delphi's) large-scale public surveys, run in partnership with Facebook
and available in aggregate form in the COVIDcast API \cite{Salomon:2021}. This
paper focuses on the COVID-19 activity indicators themselves, describing the
data streams, how they are processed and made publicly available, and insights
that can be gained by combining novel data sources with standard public health
surveillance datasets.

>>>>

The Delphi group worked with partner organizations and public data sets to build
a large-scale database of indicators tracking COVID-19 activity and other
relevant phenomena in the United States, which has been publicly available and
continuously updated since April 2020. Alongside public data on reported cases
and deaths, this database includes several unique data streams, including
indicators extracted from de-identified medical claims data, antigen test
results from a major testing manufacturer, large-scale public surveys that
measure symptoms and public behavior, and indicators based on particular Google
search queries. (We use the terms ``indicator'' and ``signal'' interchangeably.)
We make aggregate signals publicly available, generally at the county level, via
the COVIDcast API \cite{CovidcastAPI}. We store and provide access to all
previous (historical) versions of the signals, a key feature that exposes the
effects of data revisions. Moreover, we provide R \cite{CovidcastR} and Python 
\cite{CovidcastPy} packages to facilitate interaction with the API, and an
online dashboard to visualize the data \cite{CovidcastViz}.

In a companion paper, we analyze the utility provided by a core set of the
indicators in short-term COVID-19 forecasting and hotspot prediction models 
\cite{McDonald:2021}. In another companion paper, we elaborate on our research
group's (Delphi's) large-scale public surveys, run in partnership with Facebook
and available in aggregate form in the COVIDcast API \cite{Salomon:2021}. This
paper focuses on the COVID-19 indicators themselves, describing the
data streams, how they are processed and made publicly available, and insights
that can be gained by combining novel data sources with standard public health
surveillance data.
